Supplementary Figures

### 2020-01-30 supplementary_figures/supp4_selection.Rmd
added figure on nb of clusters, updated suppl

```{r, fig.width=8, fig.height=9, results="hide", warnings=FALSE, messages=FALSE}
plot_grid(plotlist=ll, ncol=2)
```

@@

```{r, include=FALSE}
ll <- lapply(names(gi), FUN=function(x){
  cumVE2(gi[[x]], gi[[x]]$devianceExplained) + xlim(0,2000) + ggtitle(x) + ylab("cumul deviance explained") + theme(legend.position="none")
})
ll$legend <- get_legend(ll[[1]] + theme(legend.position="right"))
plot_grid(plotlist=ll, ncol=2)
```

```{r, fig.width=8, fig.height=9, results="hide", warnings=FALSE, messages=FALSE}
plot_grid(plotlist=ll, ncol=2)
```

>>>>

```{r, fig.width=8, fig.height=9, results="hide", warnings=FALSE, messages=FALSE}
suppressWarnings(plot_grid(plotlist=ll, ncol=2))
```

@@

```{r, include=FALSE}
ll <- lapply(names(gi), FUN=function(x){
  cumVE2(gi[[x]], gi[[x]]$devianceExplained) + xlim(0,2000) + ggtitle(x) + ylab("cumul deviance explained") + theme(legend.position="none")
})
ll$legend <- get_legend(ll[[1]] + theme(legend.position="right"))
```

```{r, fig.width=8, fig.height=9, results="hide", warnings=FALSE, messages=FALSE}
suppressWarnings(plot_grid(plotlist=ll, ncol=2))
```

### 2020-01-30 supplementary_figures/supp6_clust.Rmd
added figure on nb of clusters, updated suppl

```{r, include=FALSE}
#res <- readRDS("../data/clust_endSummary.rds")
res <- readRDS("../data/results_clust_2.rds")
res <- parsePipNames(res$clustering)
res <- res[which(res$norm=="norm.seurat" & res$resolution <5),]
x <- grep("true\\.nbClusts",colnames(res),value=TRUE)
names(x) <- x <- sapply(strsplit(x," "),FUN=function(x) x[[1]])
y <- cbind(res[,c("k","steps","resolution","clustmethod","dims")],sapply(x, FUN=function(x){
  res[[paste(x,"n_clus")]] - res[[paste(x,"true.nbClusts")]]
}))
y$param <- ifelse( res$clustmethod=="clust.seurat", paste0(" res=",res$resolution), paste0(" steps=",res$steps))
ag <- aggregate(y[,names(x)], by=y[,c("clustmethod", "k","param"),drop=FALSE], FUN=mean)
agl <- cbind(ag[rep(1:nrow(ag), 9),1:3], dataset=rep(colnames(ag)[4:ncol(ag)], each=nrow(ag)), delta=as.numeric(as.matrix(ag[,4:ncol(ag)])))
agl$k <- factor(agl$k, as.character(sort(unique(agl$k))))
x <- sapply(unique(strsplit(ag$param, "=")), FUN=function(x) as.numeric(x[[2]]) )
names(x) <- unique(ag$param)
agl$param <- factor(agl$param, names(sort(x)))

>>>>

```{r, include=FALSE}
#res <- readRDS("../data/clust_endSummary.rds")
res <- readRDS("../data/results_clust_2.rds")
res <- parsePipNames(res$clustering)
x <- grep("true\\.nbClusts",colnames(res),value=TRUE)
names(x) <- x <- sapply(strsplit(x," "),FUN=function(x) x[[1]])
aris <- as.data.frame(rbindlist(lapply(x, FUN=function(x){
  x <- res[,paste(x,"ARI"),drop=FALSE]
  colnames(x) <- "ARI"
  x
}), idcol = "dataset"))
aris$nbClusters <- unlist(lapply(x, FUN=function(x) res[,paste(x,"n_clus")]))
aris$clust.method <- res$clustmethod
aris$norm.method <- res$norm
levels(aris$norm.method) <- c("norm.seurat","sctransform")
aris <- aris[which(aris$nbClusters <= 40),]
dd <- data.frame( dataset=names(x), k=sapply(x, FUN=function(x) res[,paste(x,"true.nbClusts")][1]))
```

```{r, fig.width=7.5, fig.height=7}
ggplot(aris, aes(nbClusters, ARI, colour=clust.method, shape=norm.method)) + 
  geom_point() + xlim(c(1,40)) + facet_wrap(~dataset) + xlab("Number of clusters") +
  geom_vline(aes(xintercept=k), data=dd, linetype="dashed") + theme(legend.position="bottom") + 
  guides(colour=guide_legend(ncol=1, title = ""), shape=guide_legend(ncol=1, title=""))
```

### Supplementary Figure `r getFigNb()`
The number of clusters called has a much bigger impact on the Adjusted Rand Index (ARI) than differences between methods. The dashed line indicates the true number of clusters.

```{r, include=FALSE}
res <- res[which(res$norm=="norm.seurat" & res$resolution <5),]
x <- grep("true\\.nbClusts",colnames(res),value=TRUE)
names(x) <- x <- sapply(strsplit(x," "),FUN=function(x) x[[1]])
y <- cbind(res[,c("k","steps","resolution","clustmethod","dims")],sapply(x, FUN=function(x){
  res[[paste(x,"n_clus")]] - res[[paste(x,"true.nbClusts")]]
}))
y$param <- ifelse( res$clustmethod=="clust.seurat", paste0(" res=",res$resolution), paste0(" steps=",res$steps))
ag <- aggregate(y[,names(x)], by=y[,c("clustmethod", "k","param"),drop=FALSE], FUN=mean)
agl <- cbind(ag[rep(1:nrow(ag), 9),1:3], dataset=rep(colnames(ag)[4:ncol(ag)], each=nrow(ag)), delta=as.numeric(as.matrix(ag[,4:ncol(ag)])))
agl$k <- factor(agl$k, as.character(sort(unique(agl$k))))
x <- sapply(unique(strsplit(ag$param, "=")), FUN=function(x) as.numeric(x[[2]]) )
names(x) <- unique(ag$param)
agl$param <- factor(agl$param, names(sort(x)))

### 2020-01-30 supplementary_figures/supp_figures.tex
added figure on nb of clusters, updated suppl

  \title{Supplementary Figures}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Pierre-Luc Germain}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{29 Januar, 2020}

@@

\begin{verbatim}
## Warning: Removed 328867 rows containing missing values (geom_path).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 302113 rows containing missing values (geom_path).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 101276 rows containing missing values (geom_path).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 68502 rows containing missing values (geom_path).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 94976 rows containing missing values (geom_path).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 101101 rows containing missing values (geom_path).
\end{verbatim}

\begin{verbatim}
## Warning: Removed 96012 rows containing missing values (geom_path).
\end{verbatim}

@@

>>>>

  \title{Supplementary Figures}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Pierre-Luc Germain}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{30 Januar, 2020}

@@

@@

The number of clusters called has a much bigger impact on the Adjusted
Rand Index (ARI) than differences between methods. The dashed line
indicates the true number of clusters.

\hypertarget{supplementary-figure-18}{%
\section{Supplementary Figure 18}\label{supplementary-figure-18}}

\includegraphics{supp_figures_files/figure-latex/unnamed-chunk-33-1.pdf}

\hypertarget{supplementary-figure-18-1}{%
\subsubsection{Supplementary Figure
18}\label{supplementary-figure-18-1}}
